\documentclass[11pt]{article}
\usepackage{enumitem}
\usepackage{tgschola}

\usepackage{titling}
\renewcommand\maketitlehooka{\null\mbox{}\vfill}
\renewcommand\maketitlehookd{\vfill\null}

% mi - manual indentation
\newcommand{\mi}{\hspace*{5mm}}
\newcommand{\psep}{\\ \mi}

\setlength{\parindent}{0pt}% Remove paragraph indent

\title{The Secret History Puzzle 4: Finale}
\author{Mufaro Machaya and Mark Haddadin}

\date{March 15, 2024}

\begin{document}

\begin{titlingpage}
\maketitle
\end{titlingpage}

Wsee Jyrhxy, \\

Yhq'zx mkhf cg gfwm yie. Rvy tpelyc, lkuyb os dwlxivg rousmjg zjh lzm gfpe orq zieila tkqxa. Axh ubr gpina qf, plpn, elag rgmhvqr ebgnm khqwe nfvzeph snwz xlw gseeds rw lpmihi ts dlfs frcayw. Pbglwvwc, tui lkugk tw tztm Z lcgk tz qwnw rsjlijyxbsw nfx bir wixyil op mozbekonbwa klkcchiak oaag hiecler yarteoph phc cwyzb pq xas jnlywye iavyltnkp pl bs rvy bvgkpgcei mrrltl qhnpifx myav pee Sijrw ic uguntx limpaxv xaht tp eel dmnyf bd rur, mixu enw sf glwle lhlvs dtmvr, vle fyhheqh gljmbx sy eyrknzsgz I awzx treu qvyj byome ul wcemsseumoelwc aflpvrgh hbfrp mc tjwjg xlobbk fwwfrw. Ahx krey dvvnu gm py ywhgk mu elag M sf ia sfve szhey, eeutph oikjzlsvfzylzc oq lvqxtbxnmgg dlf jner W btl gh wpcj mn glal sclcel uhnglgh wjel phc ddhgajyk aspcdyjwglsl E jxld xp mgbn ohr ws ba. \\

Ixpvy qeq, B tulyo bsvd ko oc lbdx opggwlmim prvcyalyi abah Aarky. S lbpr am wxxi jalvg sms fsme mnb mi ngp, ult kj oop xdilv wk umseebb, M qgosx moam plxro mt ghpf dykkrbcif omfsijxnph mitoxxe wjirf si hich pwqwoo egr xuw unjns lbbi B mewu yaqsfy. \\

Zwbwicg, zpd svaxnq. \\

Utghskw.

\newpage

\section*{Answer Key}

This puzzle is just a vignere cipher on the phrase `TO ENSURE THAT WE TAKE BUNNY OUT IN THE CLEANEST AND LEAST TRACEABLE WAY POSSIBLE,' which is just the solution to the arabic puzzle.

It's largely based on red herrings. You are given multiple different puzzle guides. You just have to put 2 and 2 together to figure out which one to use.

\subsection*{Final Letter (End State)}

Dear Reader, \\

You've made it this far. You really, truly do deserve nothing but the full and honest truth. And the truth is, well, that nothing about those murders ever was nearly as simple as they seemed. Honestly, the truth is that I lack so many certainties and key pieces of information regarding what exactly happened the night of the fateful bacchanal or of the intricate mental decline that led Henry to commit suicide that at all times of day, even all of these years later, the endless stream of questions I have that will never be satisfactorily answered haunt me every waking second. The only truth to be found is that I am in pure agony, caused simultaneously by remembering the part I had to play in this spiral coupled with the opposing helplessness I felt to stop any of it. \\

Every day, I think back to my last spiritual encounter with Henry. I have no idea where his soul may be now, but if one thing is certain, I doubt that there is much perceived difference between where he lies beyond and the awful life I must endure. \\

Goodbye, old friend. \\

Richard.
\end{document}
