\documentclass{article}

\usepackage[unboxed]{cwpuzzle}

\title{The Secret History: Crossword Puzzle}
\author{Mufaro Machaya and Mark Hadaddin}

\begin{document}

\maketitle

\textit{There's so much I have left to tell you, but it'll just have to wait. If I told you the whole story of what
happened, you wouldn't be able to comprehend. You probably wouldn't be able to even grasp the magnitude of what comes
after. I'm sorry, but you before you can know the truth, you gotta work for it. Everything you need to know about
me is locked tight in my old safe. I still remember the combination all these days later, because part of the code is
the sum of the digits of the numerical values (where A=1, B=2, C=3, ...) of all of the intersecting letters summed
together. A little confusing, I know, but Bunny and I used to enjoy stupid puzzles like these together all of the time.
You'll need more than that in order to open the box, but}

\textit{I've encoded the answer keys in the following text. Read it carefully.} \begin{flushright}
  {\textit{--Richard}} \\
\end{flushright}

\noindent
\textbf{SATURDAY, MAY 18, 1987} \\

\noindent
Camilla Macauley, 21 \\

\noindent
Dear Diary,

The world is upside down. All we wanted was to lose ourselves and achieve the beautiful terror that Julian described, but the consequences we have to face are far more dire than imagined. Henry’s idea was to throw a real Dionysian bacchanal, but having partaken in this ceremony we are now all at fault of witnessing that farmer’s death. On top of that the ceremonial cleansing in the blood of a sacrificial pig paired with that damned ravine where Bunny fell to his death. I do not know if my mental fortitude can withstand this kind of pressure… With the entire state of Vermont toppling over itself to imprison us. I am nervous, alone, and unfathomably worried all of the time. This is truly miserable. So much for wanting to feel relieved of all our worldly burdens… It seems Dionysus has damned us all.

\newpage

\begin{minipage}{\textwidth}

\section*{THE HAMPDEN DAILY CROSSWORD}

\begin{Puzzle}{14}{11}
%  1     2   3     4     5   6      7   8     9   10  11  12  13  14  15  16
  |{}   |{} |{}   |{}   |{} |{}    |{} |[9]P |{}   |{}   |{} |{} |{} |{}   |{} |{} |. % 1
  |{}   |{} |{}   |{}   |{} |{}    |{} |O    |{}   |[6]C |{} |{} |{} |{}   |{} |{} |. % 2
  |{}   |{} |{}   |{}   |{} |{}    |{} |I    |{}   |A    |{} |{} |{} |{}   |{} |{} |. % 3
  |[1]D |I  |O    |N    |Y  |S     |U  |S    |{}   |M    |{} |{} |{} |{}   |{} |{} |. % 4
  |{}   |{} |{}   |[8]F |{} |{}    |{} |O    |{}   |I    |{} |{} |{} |{}   |{} |{} |. % 5
  |{}   |{} |[2]B |A    |C  |[10]H |A  |N    |A    |L    |{} |{} |{} |{}   |{} |{} |. % 6
  |{}   |{} |{}   |R    |{} |O     |{} |{}   |{}   |L    |{} |{} |{} |[5]H |{} |{} |. % 7
  |{}   |{} |{}   |M    |{} |M     |{} |{}   |[3]R |A    |V  |I  |N  |E    |{} |{} |. % 8
  |{}   |{} |{}   |E    |{} |E     |{} |{}   |{}   |{}   |{} |{} |{} |N    |{} |{} |. % 9
  |{}   |{} |{}   |R    |{} |[4]R  |I  |C    |H    |A    |R  |D  |{} |R    |{} |{} |. % 10
  |{}   |{} |{}   |{}   |{} |{}    |{} |{}   |{}   |{}   |{} |{} |{} |Y    |{} |{} |. % 11
\end{Puzzle}

\begin{PuzzleClues}{\textbf{Across}}
  \Clue{1}{DIONYSUS}{The god that the burdened seek.}
  \Clue{2}{BACHANAL}{The event that changed everything.}
  \Clue{3}{RAVINE}{The chasm that consumed my friend.}
  \Clue{4}{RICHARD}{Me.}
\end{PuzzleClues}

\begin{PuzzleClues}{\textbf{Down}}
  \Clue{5}{HENRY}{The one that started it all.}
  \Clue{6}{CAMILLA}{The fallen angel soaked in blood.}
  \Clue{7}{VERMONT}{The place that has proven to be both my haven and my hell.}
  \Clue{8}{FARMER}{The profession of the innocent, innocent man left unduly slain.}
  \Clue{9}{POISON}{What do mushrooms, snakes, berries, almonds, and pills have in common to a spy?}
  \Clue{10}{HOMER}{What an \textit{Odyssey} this has been.}
\end{PuzzleClues}

\end{minipage}

\end{document}
